The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-15 paper.tex
update

 The fiducial run (leftmost column) specified in Section \ref{Methodology}\
 shows that the edge of the outermost bubbles is indeed a forward shock,\
 expanding roughly 14 kpc above and below the Galactic plane,\
 and with a radius of about 7 kpc along the plane, as suggested by \citet{Predehl2020}.

 \Cref{} shows the temperature profile cut at the dashed-dotted line in temperature slice.\
 The temperature profile indicates that most of the volume between the forward shock and the turbulent region\
 is around 0.3 keV \citep{Miller2016,Kataoka2018}

@@

>>>>

 The fiducial run (leftmost column) specified in Section \ref{Methodology}\
 shows that the edge of the outermost bubbles is indeed a forward shock,\
 expanding roughly 12.5 kpc above and below the Galactic plane,\
 and with a radius of about 6.8 kpc along the plane.\

 \Cref{fig__profile} shows the profiles cut at the positive z-axis in \Cref{fig__jetI5+ismSeed3-45deg}.\
 The temperature profile indicates that most of the region between the forward shock and the turbulent region\
 is around 0.3-0.4 keV \citep{Miller2016,Kataoka2018}

@@

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__profile.png}
    \caption{
             The profile along the positive z-axis in \Cref{fig__jetI5+ismSeed3-45deg}.
     }
    \label{fig__profile}
  \end{figure}
